\chapter{Implementation}\label{chap:implementation}
\todo{Jeg har ennå ikke presentert randbetingelser. Burde de inn i diskretisering eller i teorien?}We have now looked at the theoretical aspects of the level set method and constructed velocity models under the objective of approximating a curve with minimal curvature to a set of sampled points. Nothing is yet mentioned about the solution strategy and practical aspects. This chapter will answer questions concerning the technical implementation, the overall strategy chosen in this thesis, and possible pitfalls and approaches to overcome them. The entire code base for the implementation is written in Python. However, most of this chapter explains logic and algorithms which can be adapted to any preferred language.

More concrete, we will discuss spatial and temporal discretization techniques, suitable algorithms for producing the distance function and sign function, and how to prevent steep gradients from forming through a re-initialization procedure. We will first go into all aspects of the program separately and later put it all together and provide an overview of the main program.

Before moving on to the implementational details, we remind ourselves of the three models presented: the three partial differential equations we want our implementation to solve numerically.

\begin{alignat}{2}
    u_t &= |\nabla u|\,[\alpha\sigma(\mathbf{x}, t) d(\mathbf{x}; \pointsetm) + (1-\alpha) \kappa(u)], &\alpha \in \realspacem \label{eq:m1-imp}\\
    u_t &= |\nabla u|\, \bigg[\alpha \frac{ \sigma(\mathbf{x}, t)}{\beta d(\mathbf{x})+\delta} + (1-\alpha)\kappa (u) \bigg], &\alpha, \beta, \delta \in \realspacem \label{eq:m2-imp}\\
    u_t &= |\nabla u|\, \bigg[ \frac{\alpha \sigma(\mathbf{x}, t)}{\pi/2} \tan^{-1}\bigg(\frac{1}{\beta \distanceVm}\bigg) + (1-\alpha)\kappa (u) \bigg], \, &\alpha, \beta \in \realspacem \label{eq:m3-imp}
\end{alignat}

We begin with some notation concerning the discretization of the domain, \domain, and properties of the discretized problem. There are several ways to discretize the domain, and when efficiency is essential, adaptive mesh strategies or local methods can be of use. However, the focus for this project was more about investigating the behaviors of the proposed models, and the efficiency of the implementation was secondary. We thus chose a straightforward rectangular discretization.

All the sets of sampled points, \pointset, used in the following results have been fabricated data, and thus for simplicity, the domain, \domain, had been defined as $\domainm = [-1, 1]\times [-1, 1]$. The grid resolution is measured by the parameters $N_x$ and $N_y$ which is the number of nodes in respectively $x$- and $y$- direction. The corresponding grid size is then $h_x = 2/(N_x-1)$ and $h_y = 2/(N_y-1)$. 

We use the numbering of grid nodes as the convention for the Python package nympy's two-dimensional arrays. A grid point $(y_i, x_j)$ is positioned in the $i$th row counted from the bottom and $j$th column counted from the left. We have used numpy's \texttt{meshgrid} to produce the grid, which will be represented by the matrix $X$ containing both $x$- and $y$-coordinates. A grid node $(y_i, x_j)$ can thus also be represented as $X_{i, j}$. Note that this is a simplification of the \texttt{meshgrid} variables which saves the $x$- and $y$-coordinates in separate matrices $X$ and $Y$. \todo{Gå gjennom alle i og j for å sjekk at alt er riktig.}

\clearpage


\section{Temporal and Spatial Discretization} \label{sec:discretization}
This section will go through the discretization of the differential operators in the PDEs \eqref{eq:m1-imp} -- \eqref{eq:m2-imp}. This section will be rather short, as all spatial derivatives are discretized using central differences and the temporal discretization is the forward/explicit Euler method. 

Generally, we can express all models as 
\begin{equation*}
    u_t = |\nabla u| \, (\alpha f_p(\mathbf{x}) + (1-\alpha) \kappa(u)),
\end{equation*}
where $p=1, 2, 3$, and $f_p$ is the distance dependent velocity for model $p$. Expanding all terms and using \eqref{eq:curvature-u} in order to explicitly view all differential operators, this can be written as
\begin{equation}
    u_t = \alpha\, (u_x^2+u_y^2)^{1/2} f_p(\mathbf{x}) + (1-\alpha)\, \frac{u_{xx} u_y^2- 2u_{xy}u_xu_y + u_{yy}u_x^2}{(u_x^2+u_y^2)^{1/2}}.
    \label{eq:general-model-operators}
\end{equation}
We see from \eqref{eq:general-model-operators} that it is easy to switch between the different models by changing $f_p$.

From now on, when we discuss the discretization of the higher dimensional level set function, we will denote it as $U_{i, j}^{n} = u(x_j, y_i, t_n)$. 






%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\input{chapters/implementation/imp-distancefunc}
\input{chapters/implementation/imp-signfunction}
\input{chapters/implementation/imp-reinitialization}
\input{chapters/implementation/imp-datastructures}
\input{chapters/implementation/imp-mainalg}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{chapters/implementation/imp-signfunc}
%\input{chapters/implementation/imp-initialization}
%\input{chapters/implementation/imp-time-integration}
%\input{chapters/implementation/imp-stopping-criterion}




%\input{chapters/implementation/imp-space}
%\input{chapters/implementation/imp-time}

%\input{chapters/implementation/imp-signed-dist}
%\input{chapters/implementation/imp-signfunc}

